The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2017-06-30 paper/ms.tex
Text updates, adding a table of simulations

\begin{abstract}
We present the first release of the ``Galaxy Cluster Merger Catalog''. This catalog provides an extensive suite of mock observations and related data for N-body and hydrodynamical simulations of galaxy cluster mergers. These mock observations consist of projections of a number of important observable quantities in several different wavebands, for the entire evolution of each simulation as well as along different lines of sight through the three-dimensional simulation domain. The web interface to the catalog consists of easily browseable images over epoch and projection direction, as well as download links for the raw data and a JS9 interface for interactive data exploration. All of the data products are provided in the standard FITS file format, in image and table form. Data is being stored on the yt Hub~(\url{http://hub.yt}), which allows for remote access and analysis using a Jupyter notebook server. Future versions of the catalog will include simulations from a number of research groups and a variety of research topics related to the study of interactions of galaxy clusters with each other and with their member galaxies. The catalog is located at \url{http://gcmc.hub.yt}.
\end{abstract}

@@

We seek to address these issues by releasing the ``Galaxy Cluster Merger Catalog'', an extensive suite of mock observations and related data for simulations of galaxy cluster mergers. We have produced 2D projections and slices of a number of different quantities relevant to observations of galaxy clusters for a large number of merger simulations. The data products span the important stages of evolution of each merger and a number of relevant projection axes. The goal of this catalog is to provide a way to connect simulations of galaxy cluster mergers with multiwavelength observations of real merging clusters, providing an opportunity for observers to compare clusters in their observations with a particular merging scenario. The data may also be analyzed to make predictions for what various investigations of real clusters may reveal for future observations and missions.

@@

At the time of writing, the catalog contains data products from idealized binary cluster merger
simulations. {\bf The original works from which these simulations are drawn, in addition to some details of the simulations, are listed in Table \ref{tab:sim_table}.} The types of data products listed here are appropriate for such simulations. In the future, the catalog will include data products from a variety of cluster merger and related simulations, including those from cosmological simulations and simulations of interactions between clusters and their member galaxies. The types of data products are likely to expand and diversify with the inclusion of new simulations. \textbf{For more discussion of future directions for the catalog and long-term issues, see Section \ref{sec:future}}.

@@

\subsubsection{The yt Hub}\label{sec:yt_hub}
The catalog data is stored on the \code{yt Hub}\footnote{\url{https://hub.yt/}}, a conglomerate of various open source
services \textbf{hosted at the National Center for Supercomputing Applications (NCSA)}, creating an environment that allows one to collect, remotely analyze, share and publish scientific datasets. At its core, the \code{yt Hub} uses \code{Girder}\footnote{\url{https://girder.readthedocs.io}}, a data management platform that allows to transparently store, serve, and proxy data from heterogeneous backend storage engines through a single
web API. Data served by \code{Girder} can easily be gathered into dynamical hierarchies such as collections, folders and
items. This data management system is integrated with \code{JupyterHub}\footnote{\url{https://jupyterhub.readthedocs.io/}} and allows authenticated users to spawn Jupyter notebook servers with direct access to the data that is provided as a dynamically composed FUSE filesystem. Any Jupyter
notebook created in that environment during an interactive session is safely stored back in the \code{Girder} instance,
preserving the user's analysis workflow and increasing research reproducibility. In the future, we plan to have this
notebook capability integrated directly with the catalog website.

@@

\begin{itemize}
\item \code{"Tau"}: Compton optical depth of the cluster gas
\item \code{"TeSZ"}: Mass-weighted projected temperature in units of keV
\item \code{"90\_GHz"}: S-Z signal at 90~GHz in units of MJy~sr$^{-1}$
\item \code{"180\_GHz"}: S-Z signal at 180~GHz in units of MJy~sr$^{-1}$
\item \code{"240\_GHz"}: S-Z signal at 240~GHz in units of MJy~sr$^{-1}$
\end{itemize}

@@

Every simulation of a set has a ``simulation page'' which shows various quantities projected perpendicular to the merger plane for every epoch of the simulation that is available. The different epochs can be navigated using a slider bar, and buttons above the slider bar can be used to look at the same images from a different line of sight. The links attached to the images lead to the epoch pages.

\subsubsection{The Epoch Page}\label{sec:epoch_page}

Any given link on the simulation page leads to an ``epoch page'' where images from a particular simulation epoch can be examined and the corresponding data may be obtained. Links are provided to similar simulations with different input physics at the same epoch. This page also contains information about the different types of data within the files. A drop-down menu is provided for switching between the different projection axes available.

A link is provided on each epoch page to the location of the files on the \code{yt Hub}, so that one may start Jupyter notebooks with access to the data. Each epoch page also contains a JS9 application for opening the various FITS files associated with that particular epoch. A drop-down menu is provided for navigating between the various fields in each FITS file.

@@

We have made the first release of the ``Galaxy Cluster Merger Catalog'', a website designed to provide a simple yet powerful interface to accessing mock observations of galaxy cluster mergers. This release includes a suite of mock observations from a number of binary cluster merger simulations, with different initial conditions and input physics. In particular, the catalog provides a number of X-ray and S-Z synthetic observations as well as mock galaxy catalogs. Projections of the observables have been taken along a number of lines of sight through the simulation box, and at a large number of epochs for each simulation so that the merger history is well-sampled in time. This large parameter space of cluster mergers will be useful when comparing with observed cluster mergers in a number of wavebands.

@@

It is our hope that the catalog will provide a useful resource for researchers studying galaxy cluster mergers from both the perspective of current observations as well as making predictions for future missions.

@@

>>>>

\begin{abstract}
We present the first release of the ``Galaxy Cluster Merger Catalog''. This catalog provides an extensive suite of mock observations and related data for N-body and hydrodynamical simulations of galaxy cluster mergers {\bf and clusters from cosmological simulations}. These mock observations consist of projections of a number of important observable quantities in several different wavebands as well as along different lines of sight through the three-dimensional simulation domain. The web interface to the catalog consists of easily browseable images over epoch and projection direction, as well as download links for the raw data and a JS9 interface for interactive data exploration. All of the data products are provided in the standard FITS file format, in image and table form. Data is being stored on the yt Hub~(\url{http://hub.yt}), which allows for remote access and analysis using a Jupyter notebook server. Future versions of the catalog will include simulations from a number of research groups and a variety of research topics related to the study of interactions of galaxy clusters with each other and with their member galaxies. The catalog is located at \url{http://gcmc.hub.yt}.
\end{abstract}

@@

We seek to address these issues by releasing the ``Galaxy Cluster Merger Catalog'', an extensive suite of mock observations and related data for simulations of galaxy cluster mergers. We have produced 2D projections and slices of a number of different quantities relevant to observations of galaxy clusters {\bf from simulations of binary cluster mergers and cosmological simulations. The inclusion of data from both of these simulation types emphasizes the strengths of each: idealized merger simulations, due to their typically higher resolution and controlled set up, can provide insights into what kind of physics and merger configurations lead to certain observable features in cluster mergers. On the other hand, cosmological simulations capture more realistic mergers between clusters with substructure as well as cosmological accretion, providing a more direct comparison with observations.}

{\bf These data products include clusters in various stages of merging and interaction with other systems viewed along a number of relevant projection axes.} The goal of this catalog is to provide a way to connect {\bf a variety of} simulations of galaxy cluster mergers {\bf within a common interface} with multiwavelength observations of real merging clusters, providing an opportunity for observers to compare clusters in their observations with a particular merging scenario. The data may also be analyzed to make predictions for what various investigations of real clusters may reveal for future observations and missions, {\bf such as {\it Athena} and {\it Lynx}}.

@@

At the time of writing, the catalog contains data products from idealized binary cluster merger simulations {\bf and one cosmological simulation}. {\bf The original works from which these simulations are drawn, in addition to some details of the simulations, are listed in Table \ref{tab:sim_table}.} The types of data products listed here are appropriate for such simulations. In the future, the catalog will include data products {\bf from additional simulations of idealized binary mergers, cosmological simulations, and simulations of interactions between clusters and their member galaxies.} The types of data products are likely to expand and diversify with the inclusion of new simulations. \textbf{For more discussion of future directions for the catalog and long-term issues, see Section \ref{sec:future}}.

@@

\subsubsection{The yt Hub}\label{sec:yt_hub}
The catalog data is stored on the \code{yt Hub}\footnote{\url{https://hub.yt/}}, a conglomerate of various open source
services \textbf{hosted at the National Center for Supercomputing Applications (NCSA)}, creating an environment that allows one to collect, remotely analyze, share and publish scientific datasets. At its core, the \code{yt Hub} uses \code{Girder}\footnote{\url{https://girder.readthedocs.io}}, a data management platform that allows to transparently store, serve, and proxy data from heterogeneous backend storage engines through a single
web API. Data served by \code{Girder} can easily be gathered into dynamical hierarchies such as collections, folders, and
items. This data management system is integrated with \code{JupyterHub}\footnote{\url{https://jupyterhub.readthedocs.io/}} and allows authenticated users to spawn Jupyter notebook servers with direct access to the data that is provided as a dynamically composed FUSE filesystem. Any Jupyter
notebook created in that environment during an interactive session is safely stored back in the \code{Girder} instance,
preserving the user's analysis workflow and increasing research reproducibility. In the future, we plan to have this
notebook capability integrated directly with the catalog website.

@@

\begin{itemize}
\item \code{"Tau"}: Compton optical depth of the cluster gas.
\item \code{"TeSZ"}: Mass-weighted projected temperature in units of keV.
\item \code{"90\_GHz"}: S-Z signal at 90~GHz in units of MJy~sr$^{-1}$.
\item \code{"180\_GHz"}: S-Z signal at 180~GHz in units of MJy~sr$^{-1}$.
\item \code{"240\_GHz"}: S-Z signal at 240~GHz in units of MJy~sr$^{-1}$.
\end{itemize}

@@

Every simulation of a set has a ``simulation page'' which shows various quantities projected perpendicular to the merger plane for every epoch {\bf or halo} of the simulation that is available. The different epochs {\bf or halos} can be navigated using a slider bar, and buttons above the slider bar can be used to look at the same images from a different line of sight. The links attached to the images lead to the epoch {\bf or halo} pages {\bf for this simulation}.

\subsubsection{The Epoch and Halo Pages}\label{sec:epoch_page}

Any given link on the simulation page leads to an ``epoch page'' or ``halo page'' where images from a particular simulation epoch {\bf for idealized simulations, or a particular halo for cosmological simulations,} can be examined and the corresponding data may be obtained. Links are provided to similar simulations with different input physics at the same epoch {\bf or for the same halo}. This page also contains information about the different types of data within the files. A drop-down menu is provided for switching between the different projection axes available.

A link is provided on each epoch {\bf or halo} page to the location of the files on the \code{yt Hub}, so that one may start Jupyter notebooks with access to the data. Each epoch page also contains a JS9 application for opening the various FITS files associated with that particular epoch {\bf or halo}. A drop-down menu is provided for navigating between the various fields in each FITS file.

@@

We have made the first release of the ``Galaxy Cluster Merger Catalog'', a website designed to provide a simple yet powerful interface to accessing mock observations of galaxy cluster mergers. This release includes a suite of mock observations from a number of binary cluster merger simulations, with different initial conditions and input physics. In particular, the catalog provides a number of X-ray and S-Z synthetic observations as well as mock galaxy catalogs {\bf for some simulations}. Projections of the observables have been taken along a number of lines of sight through the simulation box, and at a large number of epochs for each simulation so that the merger history is well-sampled in time. This large parameter space of cluster mergers will be useful when comparing with observed cluster mergers in a number of wavebands.

@@

{\bf Comparisons of data from the catalog to current observations have already been made to useful effect by \citet{wal17} and Douglass et al. 2017, in preparation.} It is our hope that the catalog will {\bf continue to provide} a useful resource for researchers studying galaxy cluster mergers from both the perspective of current observations as well as making predictions for future missions.

@@

\bibitem[Walker et al.(2017)]{wal17} Walker, S.~A., Hlavacek-Larrondo, J., Gendron-Marsolais, M., et al.\ 2017, \mnras, 468, 2506 
